The Leaky Semicolon

### 2021-10-28 paper/related.tex
wordsmithing conclusion

There are few prior studies of relaxed memory that include sequential
composition and/or precise calculation of semantic dependencies.  No prior
work gives the semantics of sequential composition in direct style.
\citet{DBLP:conf/esop/PaviottiCPWOB20} defined \MRD{}, which calculates
dependencies using event structures rather than logic.  This strategy is
brittler than ours, leading to false positives (\textsection\ref{sec:lir}).
\citet{DBLP:journals/pacmpl/JagadeesanJR20} defined \PwP{}, using logical
entailment to define dependency.  Although \PwT{} is based on \PwP{}, there
are many differences.
Some of these are motivated by requirements unique to
\PwT{} (see \textsection\ref{sec:ex:assoc}).
% Two of these are motivated by requirements unique to
% \PwT{}: First, \PwP{} uses substitution to define read actions; \PwT{}
% Skolemizes in order to satisfy disjunction closure for predicate transformers
% (\textsection\ref{sec:ex:assoc}).  Second, \PwP{} requires \emph{consistency}
% and \emph{causal strengthening}; \PwT{} drops these in order to satisfy
% associativity (\reflem{lem:monoid}).
Other differences are stylistic: For
example, we use termination \emph{conditions} rather than termination
\emph{actions}---our formulation fixes an error in
\citeauthor{DBLP:journals/pacmpl/JagadeesanJR20}'s definition of parallel
composition.  We also fix an error in their treatment of redundant read
elimination (\textsection\ref{sec:semreg}).

>>>>

There are two prior studies of relaxed memory that include precise
calculation of semantic dependencies---neither gives the semantics of
sequential composition in direct style.
First, \citet{DBLP:conf/esop/PaviottiCPWOB20} defined \MRD{}, which calculates
dependencies using event structures rather than logic.  This strategy is
brittler than ours, leading to false positives (\textsection\ref{sec:lir}).
Second, \citet{DBLP:journals/pacmpl/JagadeesanJR20} defined \PwP{}, using logical
entailment to define dependency.  Although \PwT{} is based on \PwP{}, there
are many differences.
Some of these are motivated by requirements unique to
\PwT{} (see \textsection\ref{sec:ex:assoc}).
% Two of these are motivated by requirements unique to
% \PwT{}: First, \PwP{} uses substitution to define read actions; \PwT{}
% Skolemizes in order to satisfy disjunction closure for predicate transformers
% (\textsection\ref{sec:ex:assoc}).  Second, \PwP{} requires \emph{consistency}
% and \emph{causal strengthening}; \PwT{} drops these in order to satisfy
% associativity (\reflem{lem:monoid}).
Other differences are stylistic: For
example, we use termination \emph{conditions} rather than termination
\emph{actions}---our formulation fixes an error in
\citeauthor{DBLP:journals/pacmpl/JagadeesanJR20}'s definition of parallel
composition.  We also fix an error in their treatment of redundant read
elimination (\textsection\ref{sec:semreg}).
